%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{graphicx}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-0.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-10pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-3.5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-5pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{#2} \\
      #3 & #4 \\
    \end{tabular*}\vspace{-7pt}
}
\newcommand{\resumeSimpleHeading}[2]{
  \vspace{-5pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      {#1} & {#2} \\
    \end{tabular*}\vspace{-7pt}
}


\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-10pt}}

% Line 1: title; line 2: authors + venue; line 3: links (no year column)
\newcommand{\resumePublicationEntry}[4]{%
  \vspace{-5pt}\item
  \begin{tabular*}{0.97\textwidth}[t]{@{}p{0.97\textwidth}@{}}
    \raggedright\textbf{#1} \\
    \raggedright\small
      #2\ $\cdot$\ \textbf{#3} \\
    \raggedright\small
      #4 \\
  \end{tabular*}\vspace{-7pt}
}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.1in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=0.15in, itemsep= 0.5pt]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape Hongyang Du} \\ 
    \small 11 East Manning St, Providence, RI $|$ 
    \small 240-413-5747 $|$ 
    \small hongyangdu182@gmail.com $|$ 
    \href{https://hongyang-du.github.io/}{Website}
    $|$ \href{https://www.linkedin.com/in/hongyangdu}{LinkedIn}
    $|$ 
    \href{https://github.com/SmashedPython}{Github}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
  \resumeSubheading
      {Brown University}{Aug 2025 -- May 2027}
      {M.S. Computer Science (AI/ML Track)}{GPA 4.0/4.0}
    \resumeSubheading
      {University of Maryland, College Park}{Aug 2021 -- May 2025}
      {B.S. Computer Science (Honors), Minor in Mathematics} {GPA 3.8/4.0}
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{Professional Experience}
 \resumeSubHeadingListStart
 \resumeSimpleHeading
      {\textbf{iFlytek}-Machine Learning Engineer Intern \textbar{} Agriculture MLLM Team}{June 2024 -- Aug 2024}
    \resumeItemListStart
      \resumeItem{
        Pretrained a 2B Chinese LLM from scratch based on the LLaMA2 architecture (e.g., RoPE positional encoding, RMSNorm, SwiGLU). Employed SentencePiece Unigram tokenizer to enhance Chinese linguistic modeling.
      }
      \resumeItem{
      Combined ResNet hierarchical classification and YOLOv10 disease-spot detection to classify over 1,000 crop diseases and pests. Constructed RAG-enhanced prompts using visual clues and a knowledge graph.
      }
      \resumeItem{
        Finetuned the model using LoRA and reinforcement learning for domain-specific adaptation. Build a Chinese-centric pretraining pipeline with support for FSDP, gradient checkpointing, and customized preprocessing for Chinese text.
      }     
    \resumeItemListEnd

        
  \resumeSubHeadingListEnd
 

\section{Vision Representation}
  \resumeSubHeadingListStart
  \resumeSubheading 
      {3D Consistent Video Diffusion Model}{June 2025 -- Feb 2026}{\href{https://hongyang-du.github.io/VideoGPA-Website/}{\textbf{Preprint}}, \href{}{\textbf{CVPR 2026 Workshop}}}{}
      \resumeItemListStart
          \resumeItem{Developed a novel self-supervised framework that leverages a Geometry Foundation Model to distill 3D structural priors, addressing the long-standing challenge of temporal inconsistency and spatial drift in Video Diffusion Models.}
          \resumeItem{Introduced a training-free pipeline to automatically construct dense preference signals; by applying Direct Preference Optimization (DPO), the model effectively aligns video generation with physical geometric laws}
          \resumeItem{Significantly outperformed SOTA baselines in 3D consistency and motion coherence, achieving superior physical plausibility on complex real-world benchmarks with minimal data requirements.}

      \resumeItemListEnd
  \resumeSubheading 
      {Implicit Neural Representation for Video Compression}{May 2024 -- May 2025}
      {
      \href{https://arxiv.org/abs/2506.24127}{\textbf{WACV 2026}}
      }{}
      \resumeItemListStart
        \resumeItem{Conducted empirical study of video compression methods based on INRs. Developed a unified benchmarking platform to evaluate models across metrics PSNR, MS-SSIM, bitrate, training time, and decoding speed on HD datasets.}
        \resumeItem{Proposed a novel architecture RNeRV, which introduced a Weight Token Masking mechanism and HyperNetwork decoupling to achieve flexible bitrate control and efficient model deployment. Demonstrated +1.27\% average improvement in visual quality under equal training budgets and enhanced real-time inference throughput.
        }
        \resumeItem{Built the XINC (eXplainable INR Compression) tool to visualize neuron-level activation and contribution maps across layers and time steps, improving interpretability and facilitating model optimization for video streaming.
        }
      \resumeItemListEnd
    
    \resumeSubheading
      {Computational Geometry on Hilbert Metric Space}{Sep 2023 -- May 2024}
      {\href{https://drops.dagstuhl.de/entities/document/10.4230/LIPIcs.SoCG.2024.92}{\textbf{SoCG 2024}}
      }{}
      \resumeItemListStart
        \resumeItem{Explored Hilbert Metric Space data structures and machine learning algorithms, contributing to developing a potential new data storage paradigm in Hilbert metric coordinates.}
        \resumeItem{Engineered algorithms for generating complex geometric objects using Lua and C++. Enhanced the Ipe extensible drawing editor with efficient tools for Euclidean, Hilbert, and Funk geometric shapes.}
        
      \resumeItemListEnd


    \resumeSubHeadingListEnd



\section{VLM \& Agents}
  \resumeSubHeadingListStart
  \resumeSubheading 
      {Agent Skill Dependency-Aware Structural Retrieval}{Apr 2026}{\href{https://arxiv.org/abs/2604.05333}{\textbf{Preprint}}}{}
      \resumeItemListStart
          \resumeItem{Structured massive agent skill libraries as an offline dependency graph and retrieved small, relevant skill bundles at inference (seeding + PageRank under a token budget) instead of loading the full library.}
          \resumeItem{Reduced context tokens while improving downstream reward for LLM-based agents operating over large skill sets.}
      \resumeItemListEnd

  \resumeSubheading 
      {Self-Evolving Vision Language Models From Zero Data}{March 2025 -- June 2026}{\href{https://arxiv.org/abs/2603.09206}{\textbf{Preprint}}}{}
      \resumeItemListStart
          \resumeItem{Proposed a novel training paradigm that eliminates the need for human-annotated data ("zero data") by designing an innovative three-role collaborative pipeline: Proposer, Coder, and Solver}
          \resumeItem{Empowered the model to autonomously construct visually complex scenes via code generation; implemented Group Relative Policy Optimization (GRPO) with role-specific reward mechanisms for sequential, closed-loop training.}
          \resumeItem{Drive a comprehensive performance leap across base models (e.g., Qwen3-VL, Mimo-VL) with significant gains in multimodal understanding, mathematical reasoning, and coding capabilities.}

      \resumeItemListEnd

  \resumeSubheading 
      {Vision Language Models Understanding and Hallucination}{Jan 2025 -- Aug 2025}{\href{https://wuxiyang1996.github.io/videohallu_page/}{\textbf{NeurIPS 2025}}, 
      \href{https://openaccess.thecvf.com/content/CVPR2025W/TMM-OpenWorld/html/Li_A_Survey_of_State_of_the_Art_Large_Vision_Language_CVPRW_2025_paper.html}{\textbf{CVPR 2025 Workshop [Oral]}} }{}
      \resumeItemListStart
        \resumeItem{Designed VideoHallu dataset for hallucination detection in synthetic video understanding; proposed 2 novel metrics (temporal consistency, semantic mismatch) to quantify alignment between captions and dynamic video scenes.
        }
        \resumeItem{Implemented robust hallucination detection framework integrating frame-level caption matching, embedding similarity (CLIP/BLIP), and cross-frame alignment; enhanced via GRPO post-training with curriculum learning on video QA datasets incorporating counterintuitive commonsense and physics reasoning.
        }
        \resumeItem{Conducted a systematic survey of cutting-edge vision-language models (e.g., GPT-4V, Gemini, Qwen-VL), detailing their model architectures, instruction alignment mechanisms, and evaluation protocols.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd


\section{Publications}
  \resumeSubHeadingListStart
    \resumePublicationEntry
      {Graph of Skills: Dependency-Aware Structural Retrieval for Massive Agent Skills}
      {D. Liu*, Z. Li*, \textbf{H. Du}, et al.}
      {Preprint}
      {\href{https://arxiv.org/abs/2604.05333}{Paper} $\mid$ \href{https://github.com/davidliuk/graph-of-skills}{GitHub}}
    \resumePublicationEntry
      {A Cookbook of 3D Vision: Data, Learning Paradigms, and Application}
      {\textbf{H. Du}*, Z. Li*, D. Liu*, et al.}
      {CVPR 2026 Workshop OpenSUN3D}
      {\href{https://github.com/Hongyang-Du/awesome-3d-datasets}{GitHub}}
    \resumePublicationEntry
      {MM-Zero: Self-Evolving Multi-Model Vision Language Models From Zero Data}
      {Z. Li*, \textbf{H. Du}*, C. Huang*, et al.}
      {Preprint}
      {\href{https://arxiv.org/abs/2603.09206}{Paper} $\mid$ \href{https://github.com/zli12321/MM-Zero}{GitHub}}
    \resumePublicationEntry
      {VideoGPA: Distilling Geometry Priors for 3D-Consistent Video Generation}
      {\textbf{H. Du}*, J. Ye*, X. Cong*, et al.}
      {Preprint}
      {\href{https://arxiv.org/abs/2601.23286}{Paper} $\mid$ \href{https://hongyang-du.github.io/VideoGPA-Website/}{Web} $\mid$ \href{https://github.com/Hongyang-Du/VideoGPA}{GitHub}}
    \resumePublicationEntry
      {How to Design and Train Your Implicit Neural Representation for Video Compression}
      {M. Gwilliam, R. Zhang, N. Padmanabhan, \textbf{H. Du}, et al.}
      {WACV 2026}
      {\href{https://arxiv.org/abs/2506.24127}{Paper} $\mid$ \href{https://mgwillia.github.io/vinrb/}{Web} $\mid$ \href{https://github.com/mgwillia/vinrb}{GitHub}}
    \resumePublicationEntry
      {VideoHallu: Evaluating and Mitigating Multi-modal Hallucinations for Synthetic Videos}
      {Z. Li*, X. Wu*, Y. Qin, \textbf{H. Du}, et al.}
      {NeurIPS 2025}
      {\href{https://arxiv.org/abs/2505.01481}{Paper} $\mid$ \href{https://wuxiyang1996.github.io/videohallu_page/}{Web} $\mid$ \href{https://github.com/zli12321/VideoHallu}{GitHub}}
    \resumePublicationEntry
      {A Survey of State of the Art Large Vision Language Models: Alignment, Benchmark, Evaluations and Challenges}
      {Z. Li*, X. Wu*, \textbf{H. Du}, et al.}
      {CVPR 2025 Workshop TMM-OpenWorld [Oral]}
      {\href{https://openaccess.thecvf.com/content/CVPR2025W/TMM-OpenWorld/html/Li_A_Survey_of_State_of_the_Art_Large_Vision_Language_CVPRW_2025_paper.html}{Paper} $\mid$ \href{https://github.com/zli12321/Awesome-VLM-Papers-And-Models}{GitHub}}
    \resumePublicationEntry
      {Ipelets for the Convex Polygonal Geometry}
      {N. Parepally, A. Chatterjee, A. Gezalyan, \textbf{H. Du}, et al.}
      {SoCG 2024}
      {\href{https://drops.dagstuhl.de/entities/document/10.4230/LIPIcs.SoCG.2024.92}{Paper} $\mid$ \href{https://archive.softwareheritage.org/browse/directory/9bd3fa80632acd54ba70aaa6d413da809ef3d73d/?origin_url=https://github.com/GeneralCoder365/umd_ipelets\&revision=a192a2a0ed086dee45ac6823bcd7892efcbabfe7\&snapshot=4669f223bd0bd8b718bbc43fb7fe8eb5e4014aa6}{Software}}
  \resumeSubHeadingListEnd

%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills \& Award}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Python, Shell, Java, C++, Bash, Go, Rust, SQL, JS/HTML/CSS, OCaml, Lua, Racket, React, Matlab} \\

     \textbf{Dev Stack}{: Spring Boot, Flask, Django, FastAPI, Node.js, RESTful APIs, Redis, MongoDB, Docker, Flutter, Next.js} \\

     \textbf{AI/ML Stack}{: PyTorch, TensorFlow, Transformers, scikit-learn, OpenCV, LangChain, LlamaIndex, Haystack, NumPy} \\
    \textbf{Focus Areas}{: Self-supervised Learning, Representation Learning, Reinforcement Learning, Contrastive Learning, 2D/3D Vision, Vision-Language Models, Transformers, Diffusion Models}
    \\
     \textbf{Awards}{: Robert Ma Scholarship, Break Through Tech Scholarship, Dean’s List (7 semesters), AIME Qualifier (Top 5\%), AMC 12 Top 1\% Honor Roll of Distinction, TN State Math Competition 1st Place}
    }
    
  
    }
    
 \end{itemize}
 


\end{document}
